Measurement Bias from Address Aliasing

### 2014-08-31 paper.tex
Reference blas section in outline

The rest of this paper is structured as follows: Our methodology and experimental setup is explained in the next section.
Then section \ref{sec:aliasing} introduces ``4K aliasing'', providing necessary background for interpreting the later results.
Section \ref{sec:environment} presents an analysis of how the size of environment variables causes bias, and in Section \ref{sec:heap} we go through a similar analysis for bias to heap address alignment.
Related work is discussed in Section \ref{sec:related}.
Section \ref{sec:conclusions} includes a summary and conclusion.

@@

\section{Aliasing in Real Applications}
To investigate how real world applications can be impacted by aliasing, we look at low level numerical applications.
Basic Linear Algebra Subroutines (BLAS) is the de facto standard API for high performance linear algebra routines, with several heavily optimized implementations available~\cite{Blackford:2002:UpdatedBLAS}.
The functionality is divided into three categories:
\begin{describe}{{pad}}
  \item[\emph{Level 1}.] Scalar and vector operations, such as dot product and vector addition.
  \item[\emph{Level 2}.] Matrix-vector operations, such as gemv for general matrix-vector multiplication.
  \item[\emph{Level 3}.] Matrix-matrix operations, including the widely applied gemm routine for general matrix multiplication.
\end{describe}
Procedures operating on vectors, from level 1 or 2, intuitively appears the most likely to have potential for aliasing.

>>>>

The rest of this paper is structured as follows: Our methodology and experimental setup is explained in the next section.
Then section \ref{sec:aliasing} introduces ``4K aliasing'', providing necessary background for interpreting the later results.
Section \ref{sec:environment} presents an analysis of how the size of environment variables causes bias, and in Section \ref{sec:heap} we go through a similar analysis for bias to heap address alignment.
Finally, in Section \ref{sec:blas} we look at alias in BLAS libraries.
Related work is discussed in Section \ref{sec:related}, before we summarize and conclude in Section \ref{sec:conclusions}.

@@

\section{Aliasing in Real Applications}
\label{sec:blas}
To investigate how real world applications can be impacted by aliasing, we look at low level numerical applications.
Basic Linear Algebra Subroutines (BLAS) is the de facto standard API for high performance linear algebra routines, with several heavily optimized implementations available~\cite{Blackford:2002:UpdatedBLAS}.
The functionality is divided into three categories:
\begin{describe}{{pad}}
  \item[\emph{Level 1}.] Scalar and vector operations, such as dot product and vector addition.
  \item[\emph{Level 2}.] Matrix-vector operations, such as gemv for general matrix-vector multiplication.
  \item[\emph{Level 3}.] Matrix-matrix operations, including the widely applied gemm routine for general matrix multiplication.
\end{describe}
Procedures operating on vectors, from level 1 or 2, intuitively appears the most likely to have potential for aliasing.
